TBD

### 2021-02-24 outputs/paper/paper.Rmd
Update the format of tables

  kable(chi_df,
        digits = 2,
        caption = capt,
        booktabs = T,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    footnote(symbol = "The Chi-squared statistic is significant at the 0.05 level") %>%
    kable_paper(c("striped", "hover"))
}
```

@@

```{r Q5 + Q6 Table, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?
t1 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(prior_employees = mean(Q5, na.rm = TRUE, .groups = NULL))
t2 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(curr_employees = mean(Q6, na.rm = TRUE), .groups = NULL)
total <- merge(t1, t2, by = c("type"))
kable(total,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))
### T-Tests (Welch's)
#Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t3 <- t.test(control_q5, treatment_q5, paired = FALSE)
#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t4 <- t.test(control_q6, treatment_q6, paired = FALSE)
#Q5 + Q6 compiled t-test table
t_tests <- map_df(list(t3, t4), tidy)
t_tests = subset(t_tests, select = -c(alternative, method, conf.low, conf.high))
t_tests %>%  
  kable(
    col.names = c("Mean of the Differences",
                  "Mean (Employees Before Intervention)",
                  "Mean (Employees Post-Intervention)",
                  "t",
                  "p",
                  "df")

  ) %>%
  add_header_above(c(" ", "Control" = 1, "Treated" = 1, " ", " ", " ")) %>%
  kable_paper(c("striped", "hover")) %>%
  landscape()
```

>>>>

  kable(chi_df,
        digits = 2,
        caption = capt,
        booktabs = T,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    footnote(symbol = "The Chi-squared statistic is significant at the 0.05 level")
}
```

@@

```{r Q5 + Q6 Table, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?
t1 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(prior_employees = mean(Q5, na.rm = TRUE, .groups = NULL))
t2 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(curr_employees = mean(Q6, na.rm = TRUE), .groups = NULL)
total <- merge(t1, t2, by = c("type"))
kable(total,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))
### T-Tests (Welch's)
#Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t3 <- t.test(control_q5, treatment_q5, paired = FALSE)
#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t4 <- t.test(control_q6, treatment_q6, paired = FALSE)

### Q5 + Q6 compiled t-test table
t_tests <- map_df(list(t3, t4), tidy) %>%
  subset(select = -c(alternative, method, conf.low, conf.high))

# Round values
t_tests[] <- lapply(t_tests, round, 2)

# Output data table
t_tests %>%
  kable(
    booktabs = T,
    col.names = c("Mean Difference",
                  "Mean (Pre-Intervention)",
                  "Mean (Post-Intervention)",
                  "t",
                  "p",
                  "df")

  ) %>%
  add_header_above(c(" ", "Control" = 1, "Treated" = 1, " ", " ", " "))
```
